### 2016-07-28 paper.tex
Added derivation for resolution of conflict cells using closed solution

\usepackage{egweblnk}
\usepackage{cite}
\usepackage{balance}

@@

\title[PGVD]%
      {An Adaptive, Parallel Algorithm for Approximating the Generalized Voronoi Diagram}

@@

\begin{abstract}
We present a parallel algorithm that approximates the Generalized Voronoi Diagram (GVD) on arbitrary collections of 2D or 3D geometric objects. Our algorithm is hierarchical, not uniformly gridded, enabling us to compute the GVD on datasets with extremely close object tolerances, including intersections. We demonstrate our method on a variety of data and show example applications of the GVD in 2D and 3D. \\

@@

\red{The generalized Voronoi diagram (GVD) is an important structure that divides space into a complex of generalized Voronoi cells (GVCs) around objects.  Similar to the ordinary Voronoi diagram, each GVC contains exactly one object, or site, and every point in the GVC is closer to its contained object than to any other object.  The generalized Voronoi diagram is the boundary of the cell complex, and thus every point on the GVD is equidistant from two or more closest objects.  Applications of the GVD range from motion path planning to GIS analysis to mosaicking.

@@

We present an algorithm to compute a GVD approximation on arbitrary datasets, including those with closely spaced objects.  The approach applies a distance transform over an octree representation of the objects.  Our octree, its associated data structure, and our distance transform are novel and optimized to GVD \red{approximation. For the remainder of the paper, ``GVD'' will refer to the approximated Generalized Voronoi Diagram.}

This paper demonstrates GVD computation on data beyond the computational abilities of previous algorithms, unlocking interesting and important applications.  Our approach allows GVD-based proximity queries and other applications using a larger class of meaningful datasets.
}

\paragraph{Main contributions} The primary technical contributions described in the paper are as follows.

\begin{enumerate}
\item Contribution 1
\item Contribution 2
\item Contribution 3
\end{enumerate}

We demonstrate various applications of the GVD...

Our GVD algorithm has a few main steps: 1) ...

@@

%-----------------------------------------------------------
% Build octree
%-----------------------------------------------------------
\section{Build octree}
\label{sec:build-octree}
\red{Our algorithm works in both 2D and 3D. Lacking a dimension-independent term, we use ``octree'' as a general term to refer to both quadtrees and octrees.}

In the algorithm below, we use the Karras algorithm as a subroutine. It takes vertices of the objects as data points. Given enough parallel units, it runs in $O(\log{N})$ time, where $N$ is the number of vertices.

We use $\container{l}{O}$ to denote the smallest octree cell in octree $O$ that fully contains the geometric object $l$. The complexity of the $\container{l}{O}$ function is $O(\log{N})$. Thus, step 2 of the algorithm (lines \ref{alg:octree_containing_begin}-\ref{alg:octree_containing_end}) runs in $O(\log{N})$ time.

Step 3 of the algorithm (lines \ref{alg:octree_intersections_begin}-\ref{alg:octree_intersections_end}) runs in $O(L)$ time, where $L$ is the number of lines in all objects. Even though the loop is doubly-nested, each line is stored in a unique internal node, so no more than $L$ lines will be visited in the loops. In practice, far fewer than $L$ lines will be checked for each leaf cell, because most datasets have lines that are completely contained in internal cells that are reasonably low in the tree.

Steps 1-3 are $O(\log{N}+L) = O(2L) = O(L)$. However, average case is $O(\log{N})$, considering that most lines are contained entirely in a cell at reasonably low depth.

@@

@@

\algorithmspace
\begin{algorithm}
  \DontPrintSemicolon
  \LinesNumbered
  \KwIn{Objects, Vertices}
  \BlankLine
  \tcp{1. Build initial octree IOctree}
  IOctree := karras(Vertices)\;

  \tcp{2. Find containing internal cells}
  \ForPar{line l in Objects}{
    \label{alg:octree_containing_begin}
    c := $\container{l}{IOctree}$\;
    c.numLines++\;
  }
  Allocate c.lines using parallel prefix sums (scan)\;
  \ForPar{line l in Objects}{
    c := $\container{l}{IOctree}$\;
    c.lines.append(l)\;
  } \label{alg:octree_containing_end}
  \tcp{3. Find line-leaf cell intersections}
  \ForPar{leaf cell c in IOctree}{
    \label{alg:octree_intersections_begin}
    \ForEach{cell a in direct\_ancestors(c)}{
      \ForEach{line l in a.lines}{
        \If{l intersects c}{
          c.numLines++\;
        }
      }
    }
  }
  Allocate c.lines using parallel prefix sums (scan)\;
  \ForPar{leaf cell c in IOctree}{
    \ForEach{cell a in direct\_ancestors(c)}{
      \ForEach{line l in a.lines}{
        \If{l intersects c}{
          c.lines.append(l)\;
        }
      }
    }
  } \label{alg:octree_intersections_end}

  \tcp{4. Octree refinement}
  \ForPar{leaf cell c in IOctree}{
    c' := c\;
    \While{c' is conflict cell}{
      $(c'_0,c'_1,\dots,c'_{2^D-1})$ := subdivide c'\;
      push $(c'_0,c'_1,\dots,c'_{2^D-1})$ onto Stack\;
      c' := Stack.pop
    }
  }
\caption{BUILD\_OCTREE}
\label{alg:octree}
\end{algorithm}
\algorithmspace

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:octree-cartesian-1}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-1.pdf} }
  \subfloat[][]{
    \label{fig:octree-hierarchical-1}
    \includegraphics[width=0.48\columnwidth]{octree-hierarchical-1.pdf} } \\
  \subfloat[][]{
    \label{fig:octree-cartesian-2}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-2.pdf} }
  \subfloat[][]{
    \label{fig:octree-hierarchical-2}
    \includegraphics[width=0.48\columnwidth]{octree-hierarchical-2.pdf} }
  \caption{The $\container{l}{O}$ function finds the smallest octree cell that completely contains line $l$.
    \protect\subref{fig:octree-cartesian} Cartesian view of the octree with a red and a blue object.
    \protect\subref{fig:octree-hierarchical} Hierarchical view of the octree.
  }
  \label{fig:steps}
\end{figure}

@@

%\begin{table}
%  \centering
%  \begin{tabular}{ll}
%    \toprule
%    line &  $\container{line}{O}$ \\
%    \midrule
%    A & R \\
%    B & R \\
%    C & R \\
%    D & 20 \\
%    E & 2 \\
%    F & 2 \\
%    \bottomrule
%  \end{tabular}
%\end{table}

>>>>

\usepackage{egweblnk}
\usepackage{cite}
\usepackage{balance}
\usepackage{color}

@@

\title[PGVD]%
      {Parallel Octree Construction on Collections of Objects}

@@

\begin{abstract}
We present a parallel octree algorithm that resolves between geometric objects. The octree has the property that no octree cell intersects more than one labeled object. Previous parallel algorithms either spawn kernels hierarchically, separate points only, or make no hard guarantees of object separation. Our algorithm runs in \red{complexity?} in the average case and has excellent results in practice. We demonstrate with results on 2D and 3D datasets.

@@

The generalized Voronoi diagram (GVD) is an important structure that divides space into a complex of generalized Voronoi cells (GVCs) around objects.  Similar to the ordinary Voronoi diagram, each GVC contains exactly one object, or site, and every point in the GVC is closer to its contained object than to any other object.  The generalized Voronoi diagram is the boundary of the cell complex, and thus every point on the GVD is equidistant from two or more closest objects.  Applications of the GVD range from motion path planning to GIS analysis to mosaicking.

@@

We present an algorithm to compute a GVD approximation on arbitrary datasets, including those with closely spaced objects.  The approach applies a distance transform over an octree representation of the objects.  Our octree, its associated data structure, and our distance transform are novel and optimized to GVD approximation. For the remainder of the paper, ``GVD'' will refer to the approximated Generalized Voronoi Diagram.

This paper demonstrates GVD computation on data beyond the computational abilities of previous algorithms, unlocking interesting and important applications.  Our approach allows GVD-based proximity queries and other applications using a larger class of meaningful datasets.

Our algorithm has three steps:

\begin{enumerate}
\item Construct an octree on object vertices using Karras' algorithm \cite{karras2012maximizing}
\item Detect octree cells that intersect more than one object, which we call ``conflict cells'' (contribution)
\item Subdivide conflict cells to resolve objects (contribution)
\end{enumerate}

@@

%-----------------------------------------------------------
% Build octree
%-----------------------------------------------------------
\section{Algorithm}
\label{sec:algorithm}
Our algorithm works in both 2D and 3D. Lacking a dimension-independent term, we use ``octree'' as a general term to refer to both quadtrees and octrees. We refer to object facets, which are lines in 2D and triangles in 3D.

\subsection{Resolving conflict cells}

%\begin{adjustbox}{valign=t}
\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:conflict-resolution-x}
    \includegraphics[width=0.48\columnwidth]{conflict-resolution-x.pdf} }
  \subfloat[][]{
    \label{fig:conflict-resolution-even}
    \includegraphics[width=0.48\columnwidth]{conflict-resolution-even.pdf} } \\
  \subfloat[][]{
    \label{fig:conflict-resolution-all}
    \includegraphics[width=0.48\columnwidth]{conflict-resolution-all.pdf} }
  \subfloat[][]{
    \label{fig:conflict-resolution-octree}
    \includegraphics[width=0.48\columnwidth]{conflict-resolution-octree-samples.pdf} }
  \caption{
    \protect\subref{fig:conflict-resolution-x} A conflict cell with two lines from different objects.
    \protect\subref{fig:conflict-resolution-even} Fitting boxes such that any box intersecting both lines contains at least one sample (red dots).
    \protect\subref{fig:conflict-resolution-even} Fitting boxes such that any box intersecting both lines contains at least two samples. This ensures that an octree built from the samples using Karras' algorithm (panel \protect\subref{fig:conflict-resolution-octree}) will have no leaf cells that intersect both lines, ensuring that the new octree is locally free of conflict cells.
  }
  \label{fig:conflict-resolution}
\end{figure}
%    \end{adjustbox}

%\begin{equation}
%\label{eqn:p}
%p(s) = p = p_0 + su
%\end{equation}
%\begin{equation}
%\label{eqn:q}
%q(s) = q = q_0 + tv
%\end{equation}
%\begin{equation}
%\label{eqn:a_}
%a(s) = a = |p^x-q^x| = |p^y-q^y|
%\end{equation}

\begin{align}
p(s) &= p = p_0 + su \label{eqn:p} \\
q(t) &= q = q_0 + tv \label{eqn:q}
%a(s) = a = |p^x-q^x| = |p^y-q^y| \label{eqn:a}
\end{align}
For the case that the bisecting line has slope $0 \le m \le 1$, we wish to find $a = q^x-p^x$, which results in a box that touches both lines. Given a point $p$, we find $q$ by substituting in equations \eqref{eqn:p} and \eqref{eqn:q} and solving for $t$,
\begin{equation}
\label{eqn:abc}
t = \frac{p^x+p^y-(q_0^x+q_0^y)}{v^x+v^y}
\end{equation}
Thus,
\begin{align} 
a(s) &= q^x(t) - p^x(s) \nonumber \\
   &= q_0^x + v^x\frac{p^x(s)+p^y(s)-(q_0^x+q_0^y)}{v^x+v^y} - p^x(s) \nonumber \\
%   &= \frac{q_0^xv^y-q_0^yv^x+p^yv^x-p^xv^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p^y(s)v^x-p^x(s)v^y}{v^x+v^y} \nonumber \\
   &= \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y+s(u^yv^x-u^xv^y)}{v^x+v^y} \nonumber \\
   &= s\frac{u^yv^x-u^xv^y}{v^x+v^y}+\frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y} \label{eqn:a}
\end{align}

%$a$ is the largest power of two less than or equal to $a'$:
%\begin{equation}
%\label{eqn:ghi}
%a(s) = a = 2^{\lfloor \log_2{a'} \rfloor}
%\end{equation}

As shown in figure \ref{fig:conflict-resolution}, we desire to build a sequence $S=(s_0, s_1, \dots)$ such that $p^x(s_i) = p^x(s_{i-2}) + a(s_{i-2})$. %For convenience, we split the sequence into even and odd components and define $p^x(s_i) = p^x(s_{i-2}) + a(s_{i-2})$.
That is,
\begin{align}
x_i &= x_{i-2} + a(s_{i-2}) \label{eqn:xi_init}
\end{align}
Substituting in equation \eqref{eqn:a},
\begin{equation}
x_i = x_{i-2} + s_{i-2}\frac{u^yv^x-u^xv^y}{v^x+v^y} + \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y}
\end{equation}
%\begin{align}
%x_i &= x_{i-1} + \frac{1}{v^x+v^y}(q_0^xv^y-q_0^yv^x+p^y(s_{i-1})v^x-p^x(s_{i-1})v^y)
%\end{align}
%Substituting in equation \eqref{eqn:p} and rearranging,
%\begin{align}
%x_i &= x_{i-1} + \frac{1}{v^x+v^y}(q_0^xv^y-q_0^yv^x+(p_0^y+s_{i-1}u^y)v^x-(p_0^x+s_{i-1}u^x)v^y) \\
%    &= x_{i-1} + \frac{1}{v^x+v^y}(q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y+s_{i-1}(u^yv^x-u^xv^y)) \\
%    &= x_{i-1} + s_{i-1}\frac{u^yv^x-u^xv^y}{v^x+v^y} + \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y}
%\end{align}
Substituting in equation \eqref{eqn:p},
\begin{align}
x_i &= p_0^x+s_{i-2}u^x + s_{i-2}\frac{u^yv^x-u^xv^y}{v^x+v^y} + \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{v^x+v^y} \\
    &= s_{i-2}\frac{v^x(u^x+u^y)}{v^x+v^y} + \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x+p_0^xv^x}{v^x+v^y} \label{eqn:xi}
\end{align}
We're now ready to build the sequence. From \eqref{eqn:p},
\begin{align}
s_i &= \frac{x_i-p_0^x}{u^x}
\end{align}
Substituting in equation \eqref{eqn:xi},
\begin{align}
s_i &= s_{i-2}\frac{v^x(u^x+u^y)}{u^x(v^x+v^y)} + \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{u^x(v^x+v^y)} \\
    &= \alpha s_{i-2} + \beta \label{eqn:si_rec}
\end{align}
where $\displaystyle \alpha=\frac{v^x(u^x+u^y)}{u^x(v^x+v^y)}$ and $\displaystyle \beta=\frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y}{u^x(v^x+v^y)}$.

To solve the recurrence relation \eqref{eqn:si_rec},
\begin{align}
s_{i+2} &= \alpha s_i+\beta \\
s_{i+2}-s_i &= \alpha s_i-\alpha s_{i-2} \\
s_{i+2} &= (\alpha+1) s_i-\alpha s_{i-2}
\end{align}
The characteristic polynomial is
\begin{equation}
p(t) = t^2-(\alpha+1)t + \alpha
\end{equation}
which has roots $\alpha$ and $1$. Thus,
\begin{equation}
s_i = k_1 + k_2 \alpha^i
\end{equation}
The initial condition when $i$ is even is $s_0=0$. When $i$ is odd, the initial condition will be where $s$ is halfway along the first box (it could be anywhere in the interior of the first box, but we use halfway for convenience). So from \eqref{eqn:p},
\begin{align}
s_1 &= \frac{p^x-p_0^x}{2u^x} \\
    &= \frac{a(0)}{2u^x}
\end{align}
\begin{align}
k_1^{even} = k_1^{odd} &= \beta\left(1-\frac{\alpha}{\alpha-1}\right) \\
k_2^{even} &= \frac{\beta}{\alpha-1} \\
k_2^{odd} &= \frac{a(0)}{2u^x}+\frac{\beta}{\alpha-1}
\end{align}

It is tempting to formulate the recurrance relation using a single initial condition. This would be done by replacing equation \eqref{eqn:xi_init} with
\begin{align}
x_i &= x_{i-1} + \frac{a(s_{i-1})}{2}
\end{align}
This formulation can lead to conflict cells as shown in figure \ref{fig:conflict-resolution-half}.

\begin{figure}
  \centering
  \includegraphics[width=0.48\columnwidth]{conflict-resolution-half.pdf}
  \caption{Using a single recurrence solution we can no longer guarantee that every box that intersects both lines contains at least two samples. The box in red contains only one sample, so the octree may contain conflict cells.
  }
  \label{fig:conflict-resolution-half}
\end{figure}

%With $a$ in hand, the question becomes, at what value of $s$ does $a(s)$ double? We desire to build a sequence $S=(s_0, s_1, \dots)$ such that $a(s_i) = 2a(s_{i-1})$. Substituting \eqref{eqn:p} into \eqref{eqn:a_prime} we get
%\begin{align}
%\label{eqn:klm}
%2a(s_{i-1}) &= \frac{q_0^xv^y-q_0^yv^x+(p_0^y+s_iu^y)v^x-(p_0^x+s_iu^x)v^y}{v^x+v^y} \nonumber \\
%&= \frac{q_0^xv^y-q_0^yv^x+p_0^yv^x-p_0^xv^y+s_i(u^yv^x-u^xv^y)}{v^x+v^y}
%\end{align}
%Solving for $s_i$ results in
%\begin{equation}
%\label{eqn:klm}
%s_i = \frac{2(v^x+v^y)a(s_{i-1})-q_0^xv^y+q_0^yv^x-p_0^yv^x+p_0^xv^y}{u^yv^x-u^xv^y}
%\end{equation}
%
%For $i>0$, $a(s_i)=a'(s_i)$, so we can characterize $s_i$ as a linear equation:
%\begin{align}
%s_0 &= 0 \nonumber \\
%s_1 &= 2ma(s_0)+b \nonumber \\
%s_2 &= 2^2ma(s_0)+b \nonumber \\
%\cdots \nonumber \\
%s_i &= 2^ima(s_0)+b
%\label{eqn:si}
%\end{align}
%where 
%\[m=\frac{v^x+v^y}{u^yv^x-u^xv^y}\]
%and
%\[b=\frac{-q_0^xv^y+q_0^yv^x-p_0^yv^x+p_0^xv^y}{u^yv^x-u^xv^y}\]
%%where $m=(v^x+v^y)/(u^yv^x-u^xv^y)$ and $b=(-q_0^xv^y+q_0^yv^x-p_0^yv^x+p_0^xv^y)/(u^yv^x-u^xv^y)$.
%
%The number of elements in sequence $S$ is obtained by setting equation \eqref{eqn:si} less than one and solving for $i$:
%\begin{equation}
%i < \log_2{\frac{1-b}{ma(s_0)}}
%\end{equation}

\subsection{Build octree on vertices}

We first construct an octree on the vertices of the objects, which we call the ``vertex octree''. We use Karras' algorithm \cite{karras2012maximizing} which sorts the Morton codes of the vertices in parallel, then constructs the binary radix tree in parallel. With the binary radix tree, the octree can be constructed with a single parallel call. The strength of this algorithm lies in the fact that overall performance scales linearly with the number of cores, regardless of the distribution of points. That is, even if a large number of vertices are clustered in a small area, requiring deep octree subdivision, only a constant number of parallel calls need be made. Given enough parallel units, the Karras algorithm runs in $O(\log{N})$ time, where $N$ is the number of vertices.

\subsection{Identify conflict cells}

Our end goal is to construct an octree such that no octree cell intersects more than one object. Note that a cell is allowed to intersect more than one facet, but all facets must belong to the same object, or, in other words, all facets must share the same label. It is possible, but unlikely, that the vertex octree has this property. If so, then we are done. Otherwise, we must identify subdivide conflict cells.

One naive algorithm to identify conflict cells is to process each leaf cell $c$ in parallel and store which facets intersect $c$. This is $O(N)$. Another approach is to process each facet in parallel and add it to every cell that it intersects. This is $O(k\log{N})$ where $k$ is maximum number of cells that any facet intersects. As we will show, our algorithm is $O(j + \log{N})$ where $j$ is the maximum number of facets that intersect any cell. In practice, $\log{N} > j$, making our algorithm $O(\log{N})$.

We identify conflict cells as shown in algorithm \ref{alg:find-conflict-cells}. In lines \ref{alg:octree_containing_begin}-\ref{alg:octree_containing_end}, for each internal octree cell $c$, we store all facets for which $c$ is the smallest containing cell. Since we are implementing this in a GPGPU environment, we don't have dynamic memory, so each facet must be processed twice. The first loop discovers how many facets are to be stored in each cell after which we allocate space for the facets. We use parallel prefix sums to determine the amount of space we need to allocate as well as the offsets for each internal cell. The second loop actually stores the facets.

The $\container{f}$ procedure finds the smallest octree cell that fully contains the facet $f$. A straightforward implementation of $\container{f}$ is to perform a standard octree search on the vertices of $f$ and take the smallest octree cell that contains all of them. (Note that the cell is always an internal node, since a post-condition of the Karras algorithm is that no leaf cell contains more than one vertex.) In our implementation however, we take advantage of our existing data structures. The octree cell that contains a vertex $v$ is uniquely determined by the D-tuple bits of its morton code. For example, if a 2D vertex has morton code $010010$, then the octree is traversed from the root to child $01$ to child $00$ to child $10$. To determine $\container{f}$, we find the longest common prefix (\lcp) of the vertices. Truncating the length of \lcp\,to a multiple of D, we find the smallest octree cell that contains all vertices of $f$. The complexity of $\container{f}$ is $O(\log{N})$ for both implementations. Thus, lines \ref{alg:octree_containing_begin}-\ref{alg:octree_containing_end} run in $O(\log{N})$ time.

Lines \ref{alg:octree_intersections_begin}-\ref{alg:octree_intersections_end} of the algorithm identify and store all facets that intersect with a given leaf cell $c$. Again, it is done in two steps for memory allocation purposes. Each leaf cell $c$ looks at its $O(\log{N})$ ancestors and tests all facets stored in those ancestors for intersection with $c$. Any intersecting facets get stored in $c$. These lines run in $O(F)$ time, where $F$ is the number of facets in all objects. Even though the loop is doubly-nested, each facet is stored in a unique internal node, so no more than $F$ facets will be visited in the loops. In practice, far fewer than $F$ facets will be checked for each leaf cell, because most datasets have facets that are completely contained in internal cells that are reasonably low in the tree.

The entire conflict cell detection algorithm runs in $O(\log{N}+L) = O(L)$ because $L > \log{N}$. However, average case is $O(\log{N})$, considering that most lines are contained entirely in a cell at reasonably low depth.

@@

The second procedure we use is $\directAncestors{c}$, which finds all ancestors of octree cell $c$.

@@

\algorithmspace
\begin{algorithm}
  \DontPrintSemicolon
  \LinesNumbered
  \KwIn{VertexOctree}
  \BlankLine
  \tcp{Store contained facets}
  \ForPar{facet $f$ in Objects}{
    \label{alg:octree_containing_begin}
    a := $\container{f}$\;
    a.numFacets := a.numFacets + 1\;
  }
  Allocate space for facets in internal cells\;
  \ForPar{facet $f$ in Objects}{
    a := $\container{f}$\;
    a.facets := a.facets $\cup$ f
  } \label{alg:octree_containing_end}
  \tcp{Store intersecting facets}
  \ForPar{leaf cell c in VertexOctree}{
    \label{alg:octree_intersections_begin}
    \ForEach{cell a in \directAncestors{c}}{
      \ForEach{facet $f$ in a.facets}{
        \If{$f$ intersects c}{
          c.numFacets := c.numFacets + 1\;
        }
      }
    }
  }
  Allocate space for facets in leaf cells\;
  \ForPar{leaf cell c in VertexOctree}{
    \ForEach{cell a in \directAncestors{c}}{
      \ForEach{facet $f$ in a.facets}{
        \If{$f$ intersects c}{
          c.facets := c.facets $\cup$ f\;
        }
      }
    }
  } \label{alg:octree_intersections_end}
\caption{FIND\_CONFLICT\_CELLS}
\label{alg:find-conflict-cells}
\end{algorithm}
\algorithmspace

\algorithmspace
\begin{algorithm}
  \DontPrintSemicolon
  \LinesNumbered
  \KwIn{Octree, conflict\_cells}
  \BlankLine
  \tcp{4. Octree refinement}
  \ForPar{leaf cell c in Octree}{
    c' := c\;
    \While{c' $\in$ conflict\_cells}{
      $(c'_0,c'_1,\dots,c'_{2^D-1})$ := subdivide c'\;
      push $(c'_0,c'_1,\dots,c'_{2^D-1})$ onto Stack\;
      c' := Stack.pop
    }
  }
\caption{REFINE\_OCTREE}
\label{alg:refine-octree}
\end{algorithm}
\algorithmspace

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:octree-cartesian-1}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-1.pdf} }
  \subfloat[][]{
    \label{fig:octree-cartesian-2}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-2.pdf} } \\
  \subfloat[][]{
    \label{fig:octree-cartesian-3}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-3.pdf} }
  \subfloat[][]{
    \label{fig:octree-cartesian-5}
    \includegraphics[width=0.48\columnwidth]{octree-cartesian-5.pdf} } \\
  \subfloat[][]{
    \label{fig:octree-hierarchical-1}
    \includegraphics[width=0.48\columnwidth]{octree-hierarchical-1.pdf} }
  \subfloat[][]{
    \label{fig:octree-hierarchical-2}
    \includegraphics[width=0.48\columnwidth]{octree-hierarchical-2.pdf} }
  \caption{
    \protect\subref{fig:octree-cartesian-1} A red object and a blue object.
    \protect\subref{fig:octree-cartesian-2} The vertex octree, or octree built on the object vertices using Karras' algorithm.
    \protect\subref{fig:octree-cartesian-3}, \protect\subref{fig:octree-hierarchical-1} The vertex octree with conflict cells highlighted. Note the label of an octree cell in \protect\subref{fig:octree-cartesian-3} is the concatenation of labels from root R to the leaf cell in \protect\subref{fig:octree-hierarchical-1}. This value also corresponds to the highest order bits of the morton code of any point in the cell.
    \protect\subref{fig:octree-cartesian-5}, \protect\subref{fig:octree-hierarchical-2} The octree after resolution of conflict cells.
  }
  \label{fig:steps}
\end{figure}

@@

%\begin{table}
%  \centering
%  \begin{tabular}{ll}
%    \toprule
%    line &  $\container{line}$ \\
%    \midrule
%    A & R \\
%    B & R \\
%    C & R \\
%    D & 20 \\
%    E & 2 \\
%    F & 2 \\
%    \bottomrule
%  \end{tabular}
%\end{table}
